---
title: "Supplement 2"
subtitle: "Sites of pain"
author: "Peter Kamerman" 
date: "Last knitted: `r format(Sys.Date(), '%d %B %Y')`"
mainfont: Helvetica
---

```{r setup, include = FALSE}
# Load packages
library(tidyverse)
library(skimr)
library(knitr)
library(boot)
library(lme4)

# Create figures folder
if(!dir.exists('figures')){
    dir.create('figures')
}

# Skimr options
skim <- skim_with(factor = sfl(ordered = NULL),
                  numeric = sfl(hist = NULL))

# Set knitr options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.height = 6,
                      fig.width = 7,
                      fig.path = 'figures/supplement-2/')
```

----

Note: Sites RBP and RISI removed at data cleaning stage because n < 10. 

----

# Import and check data

```{r import}
# Import
data <- read_rds('data-cleaned/data-pain-sites.rds')
demo <- read_rds('data-cleaned/data-demographics.rds')

# Check
## Pain sites 
dim(data)
names(data)
glimpse(data)

## Demographics
dim(demo)
names(demo)
glimpse(demo)
```

----

# Basic descriptive statistics

## Pain sites

```{r numerical_sites}
data %>% 
    select(-ID) %>% 
    mutate_if(is.character, factor) %>% 
    skim()
```

## Demographics

```{r numerical_demo}
demo %>% 
    select(-ID) %>% 
    mutate_if(is.character, factor) %>% 
    skim()
```

## Boostrap functions

```{r functions}
# Proportion
prop_func <- function(d, i){
    dat <- d[i, ]
    dat_vec <- dat[[1]]
    dat_prop <- mean(dat_vec == 'Yes')
    dat_prop
}
```

----

# Proportion point estimates with 95% CIs

## Process data

```{r process_prop}
# Set seed
set.seed(2020)

# Remove ID and upper_back (only one outcome -- no pain) columns
prop <- data[, !(names(data) %in% c('ID', 'Upper_back'))]

# Bootstrap CIs
prop_boot <- prop %>% 
    # Pivot to long format
    pivot_longer(cols = everything(),
                 names_to = 'site',
                 values_to = 'pain_present') %>% 
    # Add body regions
    mutate(region = case_when(
        site == 'Chest' |
            site == 'Head' |
            site == 'Throat' |
            site == 'Shoulder' ~ 'Head and upper torso',
        site == 'Lower_back' |
            site == 'Abdomen' |
            site == 'Hips' |
            site == 'Buttocks' |
            site == 'Groin' ~ 'Lower torso',
        site == 'Legs' |
            site == 'Knees' |
            site == 'Ankles.Feet' ~ 'Lower limbs',
        site == 'Arms' |
            site == 'Elbows' |
            site == 'Wrists.Hands' ~ 'Upper limbs',
        site == 'Cervical_spine' |
            site == 'Thoracic_spine' |
            site == 'Lumbosacral_spine' ~ 'Spinal column',
        TRUE ~ 'other'
    )) %>% 
    # Nest by body region and body site
    group_by(region, site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci))

# Re-nest by body region and generate figures and tables
prop_boot2 <- prop_boot %>% 
    group_by(region) %>% 
    nest() %>% 
    # Fix site labels
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(site = str_replace_all(site,
                                                        pattern = '_',
                                                        replacement = ' '),
                                 site = str_replace_all(site, 
                                                        pattern = '\\.',
                                                        replacement = ' & ')))) %>% 
    # Re-order sites by point_est
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(site = fct_reorder(site, 
                                                    point_est)))) %>% 
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = region,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = site,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci) +
                           geom_linerange(size = 1) +
                           geom_point(size = 6) +
                           coord_flip() +
                            labs(title = .y,
                                 subtitle = '(Point estimate with 95%CI)',
                                 y = 'Proportion with pain') +
                            scale_y_continuous(limits = c(0, 1)) +
                            theme_minimal(base_size = 18) +
                            theme(plot.title = element_text(size = 18),
                                  plot.subtitle = element_text(size = 12),
                                  axis.title.y = element_blank(),
                                  panel.grid = element_blank(),
                                  axis.text = element_text(colour = '#000000'),
                                  axis.line = element_line(size = 0.5),
                                  axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = region,
                         ~ .x %>% 
                             kable(caption = .y,
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by body region

```{r tabulated_prop, results = 'asis'}
walk(prop_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by body region

```{r plotted_prop}
walk(prop_boot2$plots, ~ print(.x))
```

----

# By sex

## Process data

```{r process_sex}
# Set seed
set.seed(2020)

# Select sex data
sex <- demo[, c('ID', 'Sex')]

# Join to boot_data & remove ID and Upper_back (only one outcome -- no pain)
sex <- left_join(data, sex) %>% 
    select(-ID, -Upper_back)

# Bootstrap CIs
sex_boot <- sex %>% 
    # Pivot to long format
    pivot_longer(cols = -Sex,
                 names_to = 'site',
                 values_to = 'pain_present') %>% 
    # Add body regions
    mutate(region = case_when(
        site == 'Chest' |
            site == 'Head' |
            site == 'Throat' |
            site == 'Shoulder' ~ 'Head and upper torso',
        site == 'Lower_back' |
            site == 'Abdomen' |
            site == 'Hips' |
            site == 'Buttocks' |
            site == 'Groin' ~ 'Lower torso',
        site == 'Legs' |
            site == 'Knees' |
            site == 'Ankles.Feet' ~ 'Lower limbs',
        site == 'Arms' |
            site == 'Elbows' |
            site == 'Wrists.Hands' ~ 'Upper limbs',
        site == 'Cervical_spine' |
            site == 'Thoracic_spine' |
            site == 'Lumbosacral_spine' ~ 'Spinal column',
        TRUE ~ 'other'
    )) %>% 
    # Nest by body region and body site
    group_by(Sex, region, site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci))

# Re-nest by body region and generate figures and tables
sex_boot2 <- sex_boot %>% 
    group_by(region) %>% 
    nest() %>% 
    # Fix site labels
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(site = str_replace_all(site,
                                                        pattern = '_',
                                                        replacement = ' '),
                                 site = str_replace_all(site, 
                                                        pattern = '\\.',
                                                        replacement = ' & ')))) %>% 
    # Re-order sites by point_est
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(site = fct_reorder(site, 
                                                    point_est)))) %>% 
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = region,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = site,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci,
                               fill = Sex) +
                           geom_linerange(position = position_dodge2(width = 0.6),
                                          size = 1,
                                          colour = '#000000') +
                           geom_point(shape = 21,
                                      colour = '#000000',
                                      position = position_dodge2(width = 0.6),
                                      size = 6,
                                      stroke = 1) +
                           coord_flip() +
                           labs(title = .y,
                                subtitle = '(Point estimate with 95%CI)',
                                y = 'Proportion with pain') +
                           scale_y_continuous(limits = c(0, 1)) +
                           scale_fill_manual(values = c('#000000', '#FFFFFF')) +
                           theme_minimal(base_size = 18) +
                           theme(plot.title = element_text(size = 18),
                                 plot.subtitle = element_text(size = 12),
                                 legend.title = element_blank(),
                                 legend.position = 'top',
                                 axis.title.y = element_blank(),
                                 panel.grid = element_blank(),
                                 axis.text = element_text(colour = '#000000'),
                                 axis.line = element_line(size = 0.5),
                                 axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = region,
                         ~ .x %>% 
                             kable(caption = .y,
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by age and body region

```{r tabulated_sex, results = 'asis'}
walk(sex_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by age and body region

```{r plotted_sex}
walk(sex_boot2$plots, ~ print(.x))
```

----

# By age

## Process data

```{r process_age}
# Set seed
set.seed(2020)

# Select age data
age <- demo[, c('ID', 'Age')]

# Join to boot_data & remove ID and Upper_back (only one outcome -- no pain)
age <- left_join(data, age) %>% 
    select(-ID, -Upper_back)

# Get complete cases
age <- age[complete.cases(age), ]

# Pivot and add age group categories (10 year periods)
age_boot <- age %>% 
    # Pivot to long format
    pivot_longer(cols = -Age,
                 names_to = 'site',
                 values_to = 'pain_present') %>% 
    # Add age categories
    mutate(age_group = case_when(
        Age < 28 ~ '18-27',
        Age >= 28 & Age < 38 ~ '28-37',
        Age >= 38 & Age < 48 ~ '38-47',
        Age >= 48 & Age < 58 ~ '48-57',
        Age >= 58 & Age < 68 ~ '58-67',
        Age >= 68 & Age < 78 ~ '68-77',
        Age >= 78 & Age < 88 ~ '78-87'
    )) 

# Print count per age group
age_boot %>% 
    group_by(site, age_group) %>% 
    summarise(count = n()) %>% 
    filter(site == 'Abdomen') %>% 
    ungroup() %>% 
    select(-site) %>% 
    kable(caption = 'Participant count per age group')

# Generate CIs
age_boot2 <- age_boot %>% 
    # Remove age
    select(-Age) %>% 
    # Remove categories with less than 20 counts
    filter(age_group != '68-77') %>% 
    # Nest by age group and body site
    group_by(age_group, site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci)) %>% 
    ungroup()

# Re-nest by body region and generate figures and tables
age_boot2 <- age_boot2 %>% 
    # Fix site labels
    mutate(site = str_replace_all(site,
                                  pattern = '_',
                                  replacement = ' '),
           site = str_replace_all(site, 
                                  pattern = '\\.',
                                  replacement = ' & ')) %>% 
    # Group and nest
    group_by(site) %>% 
    nest() %>% 
    # Arrange age groups
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = site,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = age_group,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci) +
                           geom_linerange(size = 1,
                                          colour = '#000000') +
                           geom_point(colour = '#000000',
                                      size = 6) +
                           labs(title = .y,
                                subtitle = '(Point estimate with 95%CI)',
                                caption = 'Age group 68-77 years removed because n = 2',
                                x = 'Age group (Years)',
                                y = 'Proportion with pain') +
                           scale_y_continuous(limits = c(0, 1)) +
                           theme_minimal(base_size = 18) +
                           theme(plot.title = element_text(size = 18),
                                 plot.subtitle = element_text(size = 12),
                                 plot.caption = element_text(size = 12),
                                 panel.grid = element_blank(),
                                 axis.text = element_text(colour = '#000000'),
                                 axis.line = element_line(size = 0.5),
                                 axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = site,
                         ~ .x %>% 
                             arrange(age_group) %>% 
                             kable(caption = str_glue('{.y} (Age group 68-77 years removed because n = 2)'),
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by age group and body site

```{r tabulated_age, results = 'asis'}
walk(age_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by age group and body site

```{r plotted_age}
walk(age_boot2$plots, ~ print(.x))
```

----

# By most recent CD4 T-cell count

## Process data

```{r process_cd4}
# Set seed
set.seed(2020)

# Select CD4 recent data
cd4 <- demo[, c('ID', 'CD4_recent')]

# Join to boot_data & remove ID and Upper_back (only one outcome -- no pain)
cd4 <- left_join(data, cd4) %>% 
    select(-ID, -Upper_back)

# Get complete cases
cd4 <- cd4[complete.cases(cd4), ]

# Pivot and add CD4 recent group categories (counts of 100)
cd4_boot <- cd4 %>% 
    # Pivot to long format
    pivot_longer(cols = -CD4_recent,
                 names_to = 'site',
                 values_to = 'pain_present') %>% 
    # Add CD4 recent categories
    mutate(cd4_group = case_when(
        CD4_recent < 100 ~ '0-99',
        CD4_recent >= 100 & CD4_recent < 200 ~ '100-199',
        CD4_recent >= 200 & CD4_recent < 300 ~ '200-299',
        CD4_recent >= 300 & CD4_recent < 400 ~ '300-399',
        CD4_recent >= 400 & CD4_recent < 500 ~ '400-499',
        CD4_recent >= 500 ~ '500+'
    )) 

# Print count per CD4 recent group
cd4_boot %>% 
    group_by(site, cd4_group) %>% 
    summarise(count = n()) %>% 
    filter(site == 'Abdomen') %>% 
    ungroup() %>% 
    select(-site) %>% 
    kable(caption = 'Participant count per CD4 group')

# Generate CIs
cd4_boot2 <- cd4_boot %>% 
    # Remove CD4 recent
    select(-CD4_recent) %>% 
    # Nest by CD4 recent group and body site
    group_by(cd4_group, site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci)) %>% 
    ungroup()

# Re-nest by body region and generate figures and tables
cd4_boot2 <- cd4_boot2 %>% 
    # Fix site labels
    mutate(site = str_replace_all(site,
                                  pattern = '_',
                                  replacement = ' '),
           site = str_replace_all(site, 
                                  pattern = '\\.',
                                  replacement = ' & ')) %>% 
    # Group and nest
    group_by(site) %>% 
    nest() %>% 
    # Arrange CD4 recent groups
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = site,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = cd4_group,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci) +
                           geom_linerange(size = 1,
                                          colour = '#000000') +
                           geom_point(colour = '#000000',
                                      size = 6) +
                           labs(title = .y,
                                subtitle = '(Point estimate with 95%CI)',
                                x = expression('CD4 group (cells.mm'^-3*')'),
                                y = 'Proportion with pain') +
                           scale_y_continuous(limits = c(0, 1)) +
                           theme_minimal(base_size = 18) +
                           theme(plot.title = element_text(size = 18),
                                 plot.subtitle = element_text(size = 12),
                                 panel.grid = element_blank(),
                                 axis.text = element_text(colour = '#000000'),
                                 axis.line = element_line(size = 0.5),
                                 axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = site,
                         ~ .x %>% 
                             arrange(cd4_group) %>% 
                             kable(caption = .y,
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by CD4 (recent) group and body site

```{r tabulated_cd4, results = 'asis'}
walk(cd4_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by CD4 (recent) group and body site

```{r plotted_cd4}
walk(cd4_boot2$plots, ~ print(.x))
```

----

# Logistic regression (generalised linear mixed model)

Note: Age treated as a continuous variable, not like the categories used in the figures shwon above.

## Process data

Extract cases with complete data for CD4 T-cell count, age, and sex.

```{r process_glm}
# Select demographic data
demo_glmm <- demo[, c('ID', 'CD4_recent', 'Sex', 'Age')] %>% 
    # Generate site codes
    mutate(Study_site = str_remove(ID,
                                   pattern = '[0-9][0-9]?[0-9]?[0-9]?[0-9]?')) %>% 
    # Set column names
    set_names(nm = c('ID', 'CD4_recent', 'Sex', 'Age', 'Study_site'))

# Process data and remove incomplete cases
data_glmm <- data %>% 
    # Join with extracted demographics data (demo_reduced)
    left_join(demo_glmm) %>% 
    # Remove upper back (only one outcome -- no pain) and ID
    select(-ID, -Upper_back) %>% 
    # Extract complete cases
    filter(complete.cases(.))

# Convert data_glm to long format
data_glmm.long <- data_glmm %>% 
    pivot_longer(cols = -c(CD4_recent, Age, Sex, Study_site),
                 names_to = 'Pain_site',
                 values_to = 'Pain_present')

# Extract vector of body sites where the proportion with pain was >= 10%
## Stops "Singular" fit warning when performing GLMM
high_prop <- data_glmm.long %>% 
    group_by(Pain_site, Pain_present) %>% 
    summarise(n = n()) %>% 
    mutate(total = sum(n),
           prop = n/total) %>% 
    filter(Pain_present == 'Yes') %>% 
    filter(prop >= 0.10) %>% 
    .$Pain_site

# Filter for pain sites selected above
data_glmm.filtered <- data_glmm.long %>% 
    filter(Pain_site %in% high_prop)
```

## Tabulate number of cases in original and GLM datasets

```{r table_1}
# Get number of cases in original data
nrow(demo_glmm)

# Get number of cases in data_reduced
nrow(data_glmm)

# Tabulate number of cases by each study sits: original vs glm
original <- demo_glmm %>%
    group_by(Study_site) %>% 
    summarise(Count1 = n()) 

glmm <- data_glmm %>% 
    group_by(Study_site) %>% 
    summarise(Count2 = n())

original %>% 
    left_join(glmm) %>% 
    kable(caption = 'Number of cases at each study site (original dataset)',
          col.names = c('Study site', 'Original', 'GLM'))
```

## Tabulate the pain sites removed

Sites removed because proportion of cases with pain at each site was < 0.1.

```{r table_2}
data_glmm.long %>% 
    filter(!Pain_site %in% high_prop) %>% 
    select(Pain_site) %>% 
    distinct() %>% 
    mutate(Pain_site = str_replace(Pain_site, 
                                   pattern = '_',
                                   replacement = ' '),
           Pain_site = str_replace(Pain_site, 
                                   pattern = '\\.',
                                   replacement = ' & ')) %>% 
    kable(caption = 'Removed pain sites',
          col.names = 'Pain sites')
```

## GLMM

```{r glmm, results = 'asis'}
# Perform GLMM on each remaining body site
glmm_mods <- data_glmm.filtered %>% 
    # Scale Age and CD4_recent
    mutate_if(is.numeric, scale) %>% 
    # Dummy code outcome variable
    mutate(Pain_present = ifelse(Pain_present == 'No',
                                 yes = 0,
                                 no = 1)) %>% 
    # Group and then nest by Pain_site
    group_by(Pain_site) %>% 
    nest() %>% 
    # Perform logistic regression
    mutate(logistic = map(.x = data,
                          ~ glmer(Pain_present ~ 
                                      Age + 
                                      Sex + 
                                      CD4_recent + 
                                      (1|Study_site),
                                data = .x,
                                family = binomial(),
                                control = glmerControl(optimizer = 
                                                           c('bobyqa', 
                                                             'bobyqa'))))) %>% 
    # Extract effect sizes and p-values
    mutate(OR = map(.x = logistic,
                    ~ exp(fixef(.x))),
           CI = map(.x = logistic,
                          ~ exp(confint.merMod(.x, 
                                               method = 'Wald')[2:5, ])),
           p_value = map(.x = logistic,
                         ~ coef(summary(.x))[, 4])) %>% 
    # Bind data into a dataframe and tabulate,
    mutate(df = pmap(.l = list(OR, CI, p_value, Pain_site),
                     ~ cbind(..1, ..2, ..3) %>% 
                         kable(caption = ..4,
                               col.names = c('OR', 'Wald lower 95%CI', 
                                             'Wald upper 95%CI', 'p-value'))))

# Print OR for fixed effects with Wald-type 95% CIs and p-values
walk(glmm_mods$df, ~print(.x))
```

----

# Session information

```{r session}
sessionInfo()
```