---
title: "Supplement 3"
subtitle: "Number of pain sites"
author: "Peter Kamerman"
date: "Last knitted: `r format(Sys.Date(), '%d %B %Y')`"
mainfont: Helvetica
---

```{r setup, include = FALSE}
# Load packages
library(lme4)
library(MASS)
library(tidyverse)
library(skimr)
library(knitr)
library(patchwork)

# Create figures folder
if(!dir.exists('figures')){
    dir.create('figures')
}

# Skimr options
skim <- skim_with(factor = sfl(ordered = NULL),
                  numeric = sfl(hist = NULL))

# Set knitr options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = 'center',
                      fig.height = 5,
                      fig.width = 6,
                      fig.path = 'figures/supplement-3/')
```

----

# Import and check data

```{r import}
# Import
data <- read_rds('data-cleaned/data-pain-sites.rds')
demo <- read_rds('data-cleaned/data-demographics.rds')

# Check
## Pain sites
dim(data)
names(data)
glimpse(data)

data %>% 
    select(-ID, -Site) %>% 
    mutate_if(is.character, factor) %>% 
    skim()

## Demographics
dim(demo)
names(demo)
glimpse(demo)

demo %>% 
    select(-ID, -Site) %>% 
    mutate_if(is.character, factor) %>% 
    skim()
```

## Add acute/chronic pain column to demographic data

```{r acute_chronic}
# Based on pain definition used in the study
## Acute assessing pain in the last 1 week or 1 month.
## Chronic assessing persistent pain in the last 3 months
demo <- demo %>% 
    mutate(Pain_def = case_when(
        Site == 'RP' |
            Site == 'NM' ~ 'Acute',
        TRUE ~ 'Chronic'
    ))

# Tabulate
demo %>% 
    select(Pain_def) %>% 
    mutate(Pain_def = factor(Pain_def)) %>% 
    skim()
```

----

# Data analysis

## Process data

```{r process_data}
# Remove upper_back (only one outcome -- no pain)
data <- data[, !(names(data) %in% c('Upper_back'))]

# Calculate number of sites per individual
pain_count <- data %>% 
    # Format as long data
    pivot_longer(cols = -c(ID, Site),
                 names_to = 'pain_site',
                 values_to = 'pain_present') %>% 
    group_by(ID) %>% 
    summarise(Count = sum(pain_present == 'Yes', na.rm = TRUE))

# Join datasets
analysis_set <- left_join(pain_count, demo)
```

## Summary statistics

### Total group

```{r total}
analysis_set %>% 
  select(Count) %>% 
  skim()
```

### For each categorical variable

#### By sex

```{r by_sex}
analysis_set %>% 
  select(Count, Sex) %>%
  group_by(Sex) %>% 
  skim()
```

#### By HAART

```{r by_haart}
analysis_set %>% 
  select(Count, ART_currently) %>%
  filter(complete.cases(.)) %>% 
  group_by(ART_currently) %>% 
  skim()
```

#### By education

```{r by_education}
analysis_set %>% 
  select(Count, Education) %>%
  filter(complete.cases(.)) %>% 
  group_by(Education) %>% 
  skim()
```

#### By employment status

```{r by_employment}
analysis_set %>% 
  select(Count, Employment_status) %>%
  filter(complete.cases(.)) %>% 
  group_by(Employment_status) %>% 
  skim()
```

#### By pain definition

```{r by_pain}
analysis_set %>% 
  select(Count, Pain_def) %>%
  group_by(Pain_def) %>% 
  skim()
```

## Exploratory plots

### Distribution of pain counts

#### Overall count frequency

```{r whole_cohort}
all <- analysis_set %>% 
    select(Count) %>% 
    filter(complete.cases(.)) %>%
    ggplot(data = .) +
    aes(Count) +
    geom_histogram(binwidth = 1,
                   colour = '#FFFFFF') +
    labs(title = 'All participants',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Count), ])})'),
         x = 'Number of sites',
         y = 'Count') +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          panel.grid = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5)); all

all <- analysis_set %>% 
    select(Count) %>% 
    filter(complete.cases(.)) %>% 
    ggplot(data = .) +
    aes(y = Count,
        x = 'All participants') +
    geom_boxplot(outlier.colour = '#FFFFFF',
                 outlier.size = 0,
                 width = 0.5) +
    geom_point(size = 2,
               shape = 21,
               position = position_jitter(height = 0.2, width = 0.2),
               fill = '#000000',
               colour = '#000000',
               alpha = 0.5) +
    labs(title = 'All participants',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Count), ])})'),
         y = 'Number of sites') +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(size = 12),
          panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5)); all
```

#### Count by sex

```{r sex}
analysis_set %>% 
    select(Count, Sex) %>% 
    filter(complete.cases(.)) %>%
    ggplot(data = .) +
    aes(Count) +
    geom_histogram(binwidth = 1,
                   colour = '#FFFFFF') +
    labs(title = 'Sex',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Sex), ])})'),
         x = 'Number of sites',
         y = 'Count') +
    facet_wrap(~Sex) +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          panel.grid = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))

sex <- analysis_set %>% 
    select(Count, Sex) %>% 
    filter(complete.cases(.)) %>% 
    ggplot(data = .) +
    aes(y = Count,
        x = Sex) +
    geom_boxplot(outlier.colour = '#FFFFFF',
                 outlier.size = 0) +
    geom_point(size = 2,
               shape = 21,
               position = position_jitter(height = 0.2, width = 0.2),
               fill = '#000000',
               colour = '#000000',
               alpha = 0.5) +
    scale_x_discrete(labels = c('Female', 'Male')) +
    labs(title = 'Sex',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Sex), ])})'),
         y = 'Number of sites') +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(size = 12),
          panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))
```

#### Count by HAART

```{r art}
analysis_set %>% 
    select(Count, ART_currently) %>% 
    filter(complete.cases(.)) %>%
    ggplot(data = .) +
    aes(Count) +
    geom_histogram(binwidth = 1,
                   colour = '#FFFFFF') +
    scale_y_continuous(limits = c(0, 150),
                       breaks = c(0, 50, 100, 150)) +
    labs(title = 'Currently on HAART',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$ART_currently), ])})'),
         x = 'Number of sites',
         y = 'Count') +
    facet_wrap(~ART_currently) +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          panel.grid = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))

haart <- analysis_set %>%
    select(Count, ART_currently) %>% 
    filter(complete.cases(.)) %>% 
    ggplot(data = .) +
    aes(y = Count,
        x = ART_currently) +
    geom_boxplot(outlier.colour = '#FFFFFF',
                 outlier.size = 0) +
    geom_point(size = 2,
               shape = 21,
               position = position_jitter(height = 0.2, width = 0.2),
               fill = '#000000',
               colour = '#000000',
               alpha = 0.5) +
    scale_x_discrete(labels = c('No', 'Yes')) +
    labs(title = 'Currently on HAART',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$ART_currently), ])})'),
         y = 'Number of sites') +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(size = 12),
          panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))
```

#### Count education

```{r edu}
analysis_set %>% 
    select(Count, Education) %>% 
    filter(complete.cases(.)) %>%
    ggplot(data = .) +
    aes(Count) +
    geom_histogram(binwidth = 1,
                   colour = '#FFFFFF') +
    scale_y_continuous(limits = c(0, 150),
                       breaks = c(0, 50, 100, 150)) +
    labs(title = 'Level of education',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Education), ])})'),
         x = 'Number of sites',
         y = 'Count') +
    facet_wrap(~Education, ncol = 2) +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          panel.grid = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))

edu <- analysis_set %>% 
    select(Count, Education) %>% 
    filter(complete.cases(.)) %>% 
    ggplot(data = .) +
    aes(y = Count,
        x = Education) +
    geom_boxplot(outlier.colour = '#FFFFFF',
                 outlier.size = 0) +
    geom_point(size = 2,
               shape = 21,
               position = position_jitter(height = 0.2, width = 0.2),
               fill = '#000000',
               colour = '#000000',
               alpha = 0.5) +
    scale_x_discrete(labels = c('Primary', 'Secondary',
                                'Tertiary')) +
    labs(title = 'Level of Education',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Education), ])})'),
         y = 'Number of sites') +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(size = 12),
          panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))
```

#### Count by employment status

```{r employment}
analysis_set %>% 
    select(Count, Employment_status) %>% 
    filter(complete.cases(.)) %>% 
    mutate(Employment_status = factor(Employment_status,
                                      levels = c('Full-time work',
                                                 'Part-time work',
                                                 'Other',
                                                 'Unemployed'),
                                      ordered = TRUE)) %>% 
    ggplot(data = .) +
    aes(Count) +
    geom_histogram(binwidth = 1,
                   colour = '#FFFFFF') +
    scale_y_continuous(limits = c(0, 150),
                       breaks = c(0, 50, 100, 150)) +
    labs(title = 'Employment status',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Employment_status), ])})'),
         x = 'Number of sites',
         y = 'Count') +
    facet_wrap(~Employment_status, ncol = 2) +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          panel.grid = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))

employment <- analysis_set %>% 
    select(Count, Employment_status) %>% 
    filter(complete.cases(.)) %>% 
    mutate(Employment_status = factor(Employment_status,
                                      levels = c('Full-time work',
                                                 'Part-time work',
                                                 'Other',
                                                 'Unemployed'),
                                      ordered = TRUE)) %>% 
    ggplot(data = .) +
    aes(y = Count,
        x = Employment_status) +
    geom_boxplot(outlier.colour = '#FFFFFF',
                 outlier.size = 0) +
    geom_point(size = 2,
               shape = 21,
               position = position_jitter(height = 0.2, width = 0.2),
               fill = '#000000',
               colour = '#000000',
               alpha = 0.5) +
    scale_x_discrete(labels = c('Full-time\nwork', 'Part-time\nwork',
                                'Other', 'Unemployed')) +
    labs(title = 'Employment status',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Employment_status), ])})'),
         caption = 'Other: receiving social grants or were students',
         y = 'Number of sites') +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(size = 12),
          panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))
```

#### Count by pain definition

```{r pain}
analysis_set %>% 
    select(Count, Pain_def) %>% 
    filter(complete.cases(.)) %>%
    ggplot(data = .) +
    aes(Count) +
    geom_histogram(binwidth = 1,
                   colour = '#FFFFFF') +
    labs(title = 'Pain definition',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Pain_def), ])})'),
         x = 'Number of sites',
         y = 'Count') +
    facet_wrap(~Pain_def) +
    coord_flip() +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          panel.grid = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))

pain_def <- analysis_set %>% 
    select(Count, Pain_def) %>% 
    filter(complete.cases(.)) %>% 
    ggplot(data = .) +
    aes(y = Count,
        x = Pain_def) +
    geom_boxplot(outlier.colour = '#FFFFFF',
                 outlier.size = 0) +
    geom_point(size = 2,
               shape = 21,
               position = position_jitter(height = 0.2, width = 0.2),
               fill = '#000000',
               colour = '#000000',
               alpha = 0.5) +
    scale_x_discrete(labels = c('Acute', 'Chronic')) +
    labs(title = 'Pain definition',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Pain_def), ])})'),
         y = 'Number of sites') +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(size = 12),
          panel.grid = element_blank(),
          axis.title.x = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))
```


## Regression analysis

### Process data 

```{r process data}
analysis_set <- analysis_set %>% 
    # Re-factor Employment_status
    mutate(Employment_status = case_when(
        Employment_status == 'Unemployed' ~ ' 1_unemployed',
        Employment_status == 'Part-time work' ~ ' 3_employed PT',
        Employment_status == 'Full-time work' ~ ' 2_employed FT',
        Employment_status == 'Other' ~ ' 4_other'
    )) %>% 
    filter(complete.cases(.))
```

### Mixed model negative binomial regression for count data

```{r mmnb}
# Null model
null <- glmer.nb(Count ~ 1 +
                       (1|Site), 
                   data = analysis_set)
    
# Full model
mod.mmnb <- glmer.nb(Count ~ Sex +
                       # Center and scale age
                       scale(Age) +
                       # Center and scale CD4
                       scale(CD4_recent) +
                       Employment_status + 
                       Education +
                       ART_currently +
                       Pain_def +
                       (1|Site), 
                   data = analysis_set)

## Fit is singular, print model to check SD of random effect 
summary(mod.mmnb)
```

### Negative binomial regression for count data

```{r nb}
# Null model
null <- glm.nb(Count ~ 1, 
               data = analysis_set)
    
# Full model
mod.nb <- glm.nb(Count ~ Sex +
                     # Center and scale age
                     scale(Age) +
                     # Center and scale CD4
                     scale(CD4_recent) +
                     Employment_status + 
                     Education +
                     ART_currently +
                     Pain_def,
                 data = analysis_set)

# Compare models
anova(null, mod.nb)

# Summary of coefficients
cbind(Estimate = coef(mod.nb)[-1], 
      confint(mod.nb)[-1, ], 
      summary(mod.nb)$coefficients[-1, 3:4]) %>% 
    kable(caption = 'Coefficients and 95% CI',
          digits = 3,
          col.names = c('Estimate', 'Lower 95%CI', 'Upper 95%CI', 
                        'z-value', 'P-value'))
```

## Publication plot 

```{r pub_plot}
# Generate plots for age and CD4
## Count by age
age <- analysis_set %>% 
    select(Count, Age) %>% 
    filter(complete.cases(.)) %>%
    ggplot(data = .) +
    aes(y = Count,
        x = Age) +
    geom_point(size = 2,
               shape = 21,
               position = position_jitter(height = 0.2, width = 0.2),
               fill = '#000000',
               colour = '#000000',
               alpha = 0.5) +
    labs(title = 'Age',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$Age), ])})'),
         x = 'Age (years)',
         y = 'Number of sites') +
    scale_x_continuous(limits = c(18, 80),
                       breaks = seq(20, 80, by = 20)) +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(size = 12),
          panel.grid = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))

## Count by CD4 T-cell count
cd4 <- analysis_set %>% 
    select(Count, CD4_recent) %>% 
    filter(complete.cases(.)) %>%
    ggplot(data = .) +
    aes(y = Count,
        x = CD4_recent) +
    geom_point(size = 2,
               shape = 21,
               position = position_jitter(height = 0.2, width = 0.2),
               fill = '#000000',
               colour = '#000000',
               alpha = 0.5) +
    labs(title = 'Recent CD4 T-cell count',
         subtitle = str_glue('(Complete cases = {nrow(analysis_set[!is.na(
                             analysis_set$CD4_recent), ])})'),
         x = expression('CD4 T-cell count (cells.mm'^-3*')'),
         y = 'Number of sites') +
    scale_x_continuous(limits = c(0, 1400),
                       breaks = seq(0, 1400, by = 400)) +
    scale_y_continuous(breaks = seq(0, 12, 4)) +
    theme_minimal(base_size = 18) +
    theme(plot.title = element_text(size = 18),
          plot.subtitle = element_text(size = 12),
          plot.caption = element_text(size = 12),
          panel.grid = element_blank(),
          axis.text = element_text(colour = '#000000'),
          axis.line = element_line(size = 0.5),
          axis.ticks = element_line(size = 0.5))

# Fix figures for patchwork plot
all2 <- all

sex2 <- sex +
  theme(axis.title.y = element_blank())

haart2 <- haart 

employment2 <- employment 

edu2 <- edu +
  theme(axis.title.y = element_blank())


pain_def2 <- pain_def +
  theme(axis.title.y = element_blank())

age2 <- age 

cd42 <- cd4 +
  theme(axis.title.y = element_blank())

pubs <- all2 + sex2 + haart2 + edu2 + employment2 + pain_def2 + age2 + cd42 +
  plot_layout(ncol = 2)

ggsave(filename = 'figures/figure_3.png',
       width = 10,
       height = 18)
```

\begin{figure}[!h]
    \center{\includegraphics[width=\textwidth]{figures/figure_4.png}}
    \caption{Number of pain sites by predictor variable}
\end{figure}

\newpage

# Session information

```{r session}
sessionInfo()
```
