---
title: "Supplement 2"
subtitle: "Sites of pain"
author: "Peter Kamerman" 
date: "Last knitted: `r format(Sys.Date(), '%d %B %Y')`"
---

```{r setup, include = FALSE}
# Load packages
library(tidyverse)
library(skimr)
library(knitr)
library(boot)
library(lme4)
library(patchwork)

# Outputs
options(scipen = 99999)

# Create figures folder
if(!dir.exists('figures')){
    dir.create('figures')
}

# Skimr options
skim <- skim_with(factor = sfl(ordered = NULL),
                  numeric = sfl(hist = NULL))

# Set knitr options
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.height = 6,
                      fig.width = 7,
                      fig.path = 'figures/supplement-2/')
```

----

# Import and check data

```{r import}
# Import
data <- read_rds('data-cleaned/data-pain-sites.rds')
demo <- read_rds('data-cleaned/data-demographics.rds')

# Check
## Pain sites 
dim(data)
names(data)
glimpse(data)

## Demographics
dim(demo)
names(demo)
glimpse(demo)
```

----

# Basic descriptive statistics

## Pain sites

```{r numerical_sites}
data %>% 
    select(-ID, -Site) %>% 
    mutate_if(is.character, factor) %>% 
    skim()
```

## Demographics

```{r numerical_demo}
demo %>% 
    select(-ID, -Site) %>% 
    mutate_if(is.character, factor) %>% 
    skim()
```

## Add acute/chronic pain column to demographic data

```{r acute_chronic}
# Based on pain definition used in the study
## Acute assessing pain in the last 1 week or 1 month.
## Chronic assessing persistent pain in the last 3 months
demo <- demo %>% 
    mutate(Pain_def = case_when(
        Site == 'RP' |
            Site == 'NM' ~ 'Acute',
        TRUE ~ 'Chronic'
    ))

# Tabulate
demo %>% 
    select(Pain_def) %>% 
    mutate(Pain_def = factor(Pain_def)) %>% 
    skim()
```

## Boostrap functions

```{r functions}
# Proportion
prop_func <- function(d, i){
    dat <- d[i, ]
    dat_vec <- dat[[1]]
    dat_prop <- mean(dat_vec == 'Yes', na.rm = TRUE)
    dat_prop
}

# Median
median_func <- function(d, i){
    dat <- d[i, ]
    dat_vec <- dat[[1]]
    dat_median <- median(dat_vec, na.rm = TRUE)
    dat_median
}
```

----

# Proportion point estimates with 95% CIs

## Process data

```{r process_prop}
# Set seed
set.seed(2020)

# Remove ID and upper_back (only one outcome -- no pain) columns
prop <- data[, !(names(data) %in% c('ID', 'Upper_back'))]

# Bootstrap CIs
prop_boot <- prop %>% 
    # Remove Site column
    select(-Site) %>% 
    # Pivot to long format
    pivot_longer(cols = everything(),
                 names_to = 'body_site',
                 values_to = 'pain_present') %>% 
    # Add body regions
    mutate(region = case_when(
        body_site == 'Chest' |
            body_site == 'Head' |
            body_site == 'Throat' |
            body_site == 'Shoulder' ~ 'Head and upper torso',
        body_site == 'Lower_back' |
            body_site == 'Abdomen' |
            body_site == 'Hips' |
            body_site == 'Buttocks' |
            body_site == 'Groin' ~ 'Lower torso',
        body_site == 'Legs' |
            body_site == 'Knees' |
            body_site == 'Ankles.Feet' ~ 'Lower limbs',
        body_site == 'Arms' |
            body_site == 'Elbows' |
            body_site == 'Wrists.Hands' ~ 'Upper limbs',
        body_site == 'Cervical_spine' |
            body_site == 'Thoracic_spine' |
            body_site == 'Lumbosacral_spine' ~ 'Spinal column',
        TRUE ~ 'other'
    )) %>% 
    # Nest by body region and body site
    group_by(region, body_site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci))

# Re-nest by body region and generate figures and tables
prop_boot2 <- prop_boot %>% 
    group_by(region) %>% 
    nest() %>% 
    # Fix site labels
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(body_site = str_replace_all(body_site,
                                                        pattern = '_',
                                                        replacement = ' '),
                                 body_site = str_replace_all(body_site, 
                                                        pattern = '\\.',
                                                        replacement = ' & '),
                                 body_site = str_replace_all(body_site,
                                                        pattern = 'Lower back',
                                                        replacement = 'Flank')))) %>% 
    # Re-order sites by point_est
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(body_site = fct_reorder(body_site, 
                                                    point_est)))) %>% 
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = region,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = body_site,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci) +
                           geom_linerange(size = 1,
                                          colour = '#000000') +
                           geom_point(shape = 21,
                                      colour = '#000000',
                                      fill = '#000000',
                                      size = 3,
                                      stroke = 1) +
                           coord_flip() +
                            labs(title = .y,
                                 subtitle = '(Point estimate with 95%CI)',
                                 y = 'Proportion with pain') +
                            scale_y_continuous(limits = c(0, 0.6)) +
                            theme_minimal(base_size = 18) +
                            theme(plot.title = element_text(size = 18),
                                  plot.subtitle = element_text(size = 12),
                                  axis.title.y = element_blank(),
                                  panel.grid = element_blank(),
                                  axis.text = element_text(colour = '#000000'),
                                  axis.line = element_line(size = 0.5),
                                  axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = region,
                         ~ .x %>% 
                             kable(caption = .y,
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by body region

```{r tabulated_prop, results = 'asis'}
walk(prop_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by body region

```{r plotted_prop, fig.height = 10, fig.width = 8}
upper <- prop_boot2$plots[[1]] +
    theme(axis.title.x = element_blank())

arm <- prop_boot2$plots[[2]] +
    theme(axis.title.x = element_blank())

lower <- prop_boot2$plots[[3]] +
    theme(axis.title.x = element_blank())

spine <- prop_boot2$plots[[4]]

leg <- prop_boot2$plots[[5]]

# Patchwork
plot_prop <- upper + lower + arm + leg + spine + 
    plot_layout(ncol = 2)

# Output
plot_prop
```

----

# By sex

## Process data

```{r process_sex}
# Set seed
set.seed(2020)

# Select sex data
sex <- demo[, c('ID', 'Sex')]

# Join to boot_data & remove ID, site, and upper_back (only one outcome -- no pain)
sex <- left_join(data, sex) %>% 
    select(-ID, -Site, -Upper_back)

# Bootstrap CIs
sex_boot <- sex %>% 
    # Pivot to long format
    pivot_longer(cols = -Sex,
                 names_to = 'body_site',
                 values_to = 'pain_present') %>% 
    # Add body regions
    mutate(region = case_when(
        body_site == 'Chest' |
            body_site == 'Head' |
            body_site == 'Throat' |
            body_site == 'Shoulder' ~ 'Head and upper torso',
        body_site == 'Lower_back' |
            body_site == 'Abdomen' |
            body_site == 'Hips' |
            body_site == 'Buttocks' |
            body_site == 'Groin' ~ 'Lower torso',
        body_site == 'Legs' |
            body_site == 'Knees' |
            body_site == 'Ankles.Feet' ~ 'Lower limbs',
        body_site == 'Arms' |
            body_site == 'Elbows' |
            body_site == 'Wrists.Hands' ~ 'Upper limbs',
        body_site == 'Cervical_spine' |
            body_site == 'Thoracic_spine' |
            body_site == 'Lumbosacral_spine' ~ 'Spinal column',
        TRUE ~ 'other'
    )) %>% 
    # Nest by body region and body site
    group_by(Sex, region, body_site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci))

# Re-nest by body region and generate figures and tables
sex_boot2 <- sex_boot %>% 
    group_by(region) %>% 
    nest() %>% 
    # Fix site labels
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(body_site = str_replace_all(body_site,
                                                        pattern = '_',
                                                        replacement = ' '),
                                 body_site = str_replace_all(body_site, 
                                                        pattern = '\\.',
                                                        replacement = ' & ')))) %>% 
    # Re-order sites by point_est
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(body_site = fct_reorder(body_site, 
                                                    point_est)))) %>% 
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = region,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = body_site,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci,
                               fill = Sex) +
                           geom_linerange(position = position_dodge2(width = 0.6),
                                          size = 1,
                                          colour = '#000000') +
                           geom_point(shape = 21,
                                      colour = '#000000',
                                      position = position_dodge2(width = 0.6),
                                      size = 4,
                                      stroke = 1) +
                           coord_flip() +
                           labs(title = .y,
                                subtitle = '(Point estimate with 95%CI)',
                                y = 'Proportion with pain') +
                           scale_y_continuous(limits = c(0, 0.6)) +
                           scale_fill_manual(values = c('#000000', '#FFFFFF')) +
                           theme_minimal(base_size = 18) +
                           theme(plot.title = element_text(size = 18),
                                 plot.subtitle = element_text(size = 12),
                                 legend.title = element_blank(),
                                 legend.position = c(0.8, 0.87),
                                 legend.background = element_rect(colour = '#000000',
                                                                  size = 0.3),
                                 axis.title.y = element_blank(),
                                 panel.grid = element_blank(),
                                 axis.text = element_text(colour = '#000000'),
                                 axis.line = element_line(size = 0.5),
                                 axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = region,
                         ~ .x %>% 
                             kable(caption = .y,
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by age and body region

```{r tabulated_sex, results = 'asis'}
walk(sex_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by age and body region

```{r plotted_sex, fig.height = 9, fig.width = 8}
sex_upper <- sex_boot2$plots[[1]] +
    theme(axis.title.x = element_blank(),
          legend.position = 'none')

sex_arm <- sex_boot2$plots[[2]] +
    theme(axis.title.x = element_blank(),
          legend.position = 'none')

sex_lower <- sex_boot2$plots[[3]] +
    theme(axis.title.x = element_blank())

sex_spine <- sex_boot2$plots[[4]] +
    theme(legend.position = 'none')

sex_leg <- sex_boot2$plots[[5]] +
    theme(legend.position = 'none')

# Patchwork
sex_prop <- sex_upper + sex_lower + sex_arm + sex_leg + sex_spine + 
    plot_layout(ncol = 2)

# Output
sex_prop

# Save
ggsave(filename = 'figures/figure_1.png', 
       plot = sex_prop,
       width = 12, 
       height = 12)
```

----

# By age

For ease of tabulation and plotting in this section of the supplement, I divided age into seven age categories. However for data analysis (see: Logistic regression, section 7), I analysed age as a continuous variable. 

## Process data

```{r process_age}
# Set seed
set.seed(2020)

# Select age data
age <- demo[, c('ID', 'Age')]

# Join to boot_data & remove ID, study site, and upper_back 
# (only one outcome -- no pain)
age <- left_join(data, age) %>% 
    select(-ID, -Site, -Upper_back)

# Get complete cases
age <- age[complete.cases(age), ]

# Pivot and add age group categories (10 year periods)
age_boot <- age %>% 
    # Pivot to long format
    pivot_longer(cols = -Age,
                 names_to = 'body_site',
                 values_to = 'pain_present') %>% 
    # Add age categories
    mutate(age_group = case_when(
        Age < 28 ~ '18-27',
        Age >= 28 & Age < 38 ~ '28-37',
        Age >= 38 & Age < 48 ~ '38-47',
        Age >= 48 & Age < 58 ~ '48-57',
        Age >= 58 & Age < 68 ~ '58-67',
        Age >= 68 & Age < 78 ~ '68-77',
        Age >= 78 & Age < 88 ~ '78-87'
    )) 

# Print count per age group
age_boot %>% 
    group_by(body_site, age_group) %>% 
    summarise(count = n()) %>% 
    filter(body_site == 'Abdomen') %>% 
    ungroup() %>% 
    select(-body_site) %>% 
    kable(caption = 'Participant count per age group')

# Generate CIs
age_boot2 <- age_boot %>% 
    # Remove age
    select(-Age) %>% 
    # Remove categories with less than 20 counts
    filter(age_group != '68-77') %>% 
    # Nest by age group and body site
    group_by(age_group, body_site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci)) %>% 
    ungroup()

# Re-nest by body region and generate figures and tables
age_boot2 <- age_boot2 %>% 
    # Fix site labels
    mutate(body_site = str_replace_all(body_site,
                                  pattern = '_',
                                  replacement = ' '),
           body_site = str_replace_all(body_site, 
                                  pattern = '\\.',
                                  replacement = ' & ')) %>% 
    # Group and nest
    group_by(body_site) %>% 
    nest() %>% 
    # Arrange age groups
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = body_site,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = age_group,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci) +
                           geom_linerange(size = 1,
                                          colour = '#000000') +
                           geom_point(colour = '#000000',
                                      size = 6) +
                           labs(title = .y,
                                subtitle = '(Point estimate with 95%CI)',
                                caption = 'Age group 68-77 years removed because n = 2',
                                x = 'Age group (Years)',
                                y = 'Proportion with pain') +
                           scale_y_continuous(limits = c(0, 1)) +
                           coord_flip() +
                           theme_minimal(base_size = 18) +
                           theme(plot.title = element_text(size = 18),
                                 plot.subtitle = element_text(size = 12),
                                 plot.caption = element_text(size = 12),
                                 panel.grid = element_blank(),
                                 axis.text = element_text(colour = '#000000'),
                                 axis.line = element_line(size = 0.5),
                                 axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = body_site,
                         ~ .x %>% 
                             arrange(age_group) %>% 
                             kable(caption = str_glue('{.y} (Age group 68-77 years removed because n = 2)'),
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by age group and body site

```{r tabulated_age, results = 'asis'}
walk(age_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by age group and body site

```{r plotted_age}
walk(age_boot2$plots, ~ print(.x))
```

----

# By most recent CD4 T-cell count

For ease of tabulation and plotting in this section of the supplement, I divided the most recent CD4 T-cell count into six categories. However for data analysis (see: Logistic regression, section 7), I analysed CD4 T-cell count as a continuous variable. 

## Process data

```{r process_cd4}
# Set seed
set.seed(2020)

# Select CD4 recent data
cd4 <- demo[, c('ID', 'CD4_recent')]

# Join to boot_data & remove ID, study site, and upper_back 
# (only one outcome -- no pain)
cd4 <- left_join(data, cd4) %>% 
    select(-ID, -Site, -Upper_back)

# Get complete cases
cd4 <- cd4[complete.cases(cd4), ]

# Pivot and add CD4 recent group categories (counts of 100)
cd4_boot <- cd4 %>% 
    # Pivot to long format
    pivot_longer(cols = -CD4_recent,
                 names_to = 'body_site',
                 values_to = 'pain_present') %>% 
    # Add CD4 recent categories
    mutate(cd4_group = case_when(
        CD4_recent < 100 ~ '0-99',
        CD4_recent >= 100 & CD4_recent < 200 ~ '100-199',
        CD4_recent >= 200 & CD4_recent < 300 ~ '200-299',
        CD4_recent >= 300 & CD4_recent < 400 ~ '300-399',
        CD4_recent >= 400 & CD4_recent < 500 ~ '400-499',
        CD4_recent >= 500 ~ '500+'
    )) 

# Print count per CD4 recent group
cd4_boot %>% 
    group_by(body_site, cd4_group) %>% 
    summarise(count = n()) %>% 
    filter(body_site == 'Abdomen') %>% 
    ungroup() %>% 
    select(-body_site) %>% 
    kable(caption = 'Participant count per CD4 group')

# Generate CIs
cd4_boot2 <- cd4_boot %>% 
    # Remove CD4 recent
    select(-CD4_recent) %>% 
    # Nest by CD4 recent group and body site
    group_by(cd4_group, body_site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci)) %>% 
    ungroup()

# Re-nest by body region and generate figures and tables
cd4_boot2 <- cd4_boot2 %>% 
    # Fix site labels
    mutate(body_site = str_replace_all(body_site,
                                  pattern = '_',
                                  replacement = ' '),
           body_site = str_replace_all(body_site, 
                                  pattern = '\\.',
                                  replacement = ' & ')) %>% 
    # Group and nest
    group_by(body_site) %>% 
    nest() %>% 
    # Arrange CD4 recent groups
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = body_site,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = cd4_group,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci) +
                           geom_linerange(size = 1,
                                          colour = '#000000') +
                           geom_point(colour = '#000000',
                                      size = 6) +
                           labs(title = .y,
                                subtitle = '(Point estimate with 95%CI)',
                                x = expression('CD4 group (cells.mm'^-3*')'),
                                y = 'Proportion with pain') +
                           scale_y_continuous(limits = c(0, 1)) +
                           coord_flip() +
                           theme_minimal(base_size = 18) +
                           theme(plot.title = element_text(size = 18),
                                 plot.subtitle = element_text(size = 12),
                                 panel.grid = element_blank(),
                                 axis.text = element_text(colour = '#000000'),
                                 axis.line = element_line(size = 0.5),
                                 axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = body_site,
                         ~ .x %>% 
                             arrange(cd4_group) %>% 
                             kable(caption = .y,
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by CD4 (recent) group and body site

```{r tabulated_cd4, results = 'asis'}
walk(cd4_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by CD4 (recent) group and body site

```{r plotted_cd4}
walk(cd4_boot2$plots, ~ print(.x))
```

----

# By pain definition

Pain in the last week or month (acute) versus persistent pain for the last 3 months (chronic)

## Process data

```{r process_pain}
# Set seed
set.seed(2020)

# Select pain data
pain <- demo[, c('ID', 'Pain_def')]

# Join to boot_data & remove ID, site, and upper_back (only one outcome -- no pain)
pain <- left_join(data, pain) %>% 
    select(-ID, -Site, -Upper_back)

# Bootstrap CIs
pain_boot <- pain %>% 
    # Pivot to long format
    pivot_longer(cols = -Pain_def,
                 names_to = 'body_site',
                 values_to = 'pain_present') %>% 
    # Add body regions
    mutate(region = case_when(
        body_site == 'Chest' |
            body_site == 'Head' |
            body_site == 'Throat' |
            body_site == 'Shoulder' ~ 'Head and upper torso',
        body_site == 'Lower_back' |
            body_site == 'Abdomen' |
            body_site == 'Hips' |
            body_site == 'Buttocks' |
            body_site == 'Groin' ~ 'Lower torso',
        body_site == 'Legs' |
            body_site == 'Knees' |
            body_site == 'Ankles.Feet' ~ 'Lower limbs',
        body_site == 'Arms' |
            body_site == 'Elbows' |
            body_site == 'Wrists.Hands' ~ 'Upper limbs',
        body_site == 'Cervical_spine' |
            body_site == 'Thoracic_spine' |
            body_site == 'Lumbosacral_spine' ~ 'Spinal column',
        TRUE ~ 'other'
    )) %>% 
    # Nest by body region and body site
    group_by(Pain_def, region, body_site) %>% 
    nest() %>% 
    # Boostrap data
    mutate(boot = map(.x = data,
                      ~ boot(data = .x,
                             statistic = prop_func, 
                             R = 999,
                             stype = 'i',
                             parallel = 'multicore',
                             ncpus = 4))) %>% 
    # Get CI
    mutate(ci = map(.x = boot,
                    ~ boot.ci(.x, type = 'perc'))) %>% 
    # Extract ci data
    mutate(point_est = map(.x = ci,
                           ~ .x$t0),
           lower_ci = map(.x = ci,
                          ~ .x$percent[[4]]),
           upper_ci = map(.x = ci,
                          ~ .x$percent[[5]])) %>% 
    # Remove columns
    select(-data, -boot, -ci) %>% 
    # Unnest
    unnest(cols = c(point_est, lower_ci, upper_ci))

# Re-nest by body region and generate figures and tables
pain_boot2 <- pain_boot %>% 
    group_by(region) %>% 
    nest() %>% 
    # Fix site labels
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(body_site = str_replace_all(body_site,
                                                        pattern = '_',
                                                        replacement = ' '),
                                 body_site = str_replace_all(body_site, 
                                                        pattern = '\\.',
                                                        replacement = ' & ')))) %>% 
    # Re-order sites by point_est
    mutate(data = map(.x = data,
                      ~ .x %>% 
                          mutate(body_site = fct_reorder(body_site, 
                                                    point_est)))) %>% 
    # Plot data
    mutate(plots = map2(.x = data,
                        .y = region,
                       ~ .x %>% 
                           ggplot(data = .) +
                           aes(x = body_site,
                               y = point_est,
                               ymin = lower_ci,
                               ymax = upper_ci,
                               fill = Pain_def) +
                           geom_linerange(position = position_dodge2(width = 0.6),
                                          size = 1,
                                          colour = '#000000') +
                           geom_point(shape = 21,
                                      colour = '#000000',
                                      position = position_dodge2(width = 0.6),
                                      size = 6,
                                      stroke = 1) +
                           coord_flip() +
                           labs(title = .y,
                                subtitle = '(Point estimate with 95%CI)',
                                y = 'Proportion with pain') +
                           scale_y_continuous(limits = c(0, 1)) +
                           scale_fill_manual(values = c('#000000', '#FFFFFF')) +
                           theme_minimal(base_size = 18) +
                           theme(plot.title = element_text(size = 18),
                                 plot.subtitle = element_text(size = 12),
                                 legend.title = element_blank(),
                                 legend.position = 'top',
                                 axis.title.y = element_blank(),
                                 panel.grid = element_blank(),
                                 axis.text = element_text(colour = '#000000'),
                                 axis.line = element_line(size = 0.5),
                                 axis.ticks = element_line(size = 0.5)))) %>% 
    # Tabulate data
    mutate(tables = map2(.x = data,
                         .y = region,
                         ~ .x %>% 
                             kable(caption = .y,
                                   digits = 2)))
```

## Tabulated proportions (with 95% CIs), by age and body region

```{r tabulated_pain, results = 'asis'}
walk(pain_boot2$tables, ~ print(.x))
```

## Plotted proportions (with 95% CIs), by age and body region

```{r plotted_pain}
walk(pain_boot2$plots, ~ print(.x))
```


# Session information

```{r session}
sessionInfo()
```